Assignment 4

### 2015-03-10 rmtw/a4/latex8.tex
Willy commit
Added reasoning for Test3

\SubSection{Test Used for H\textsubscript{Fault}}
The frequency of A, B and C faults found were tabulated against the inspection groups which found them. Any response that was not not applicable (NA) was discarded from the table. An example of this is found in table 3. In order to determine if they do find the same faults, a Chi-Square (CS) test of independence was performed on the tabulated results. The reason the CS was used was primarily because the data we wished to use were categorical and the frequency of each category was at least 5. Other tests, such as Fishers Exact Test were not applicable, for example, our table was greater than 2x2 rows. Fishers test should only be used for 2x2 tables.

>>>>

\SubSection{Test Used for H\textsubscript{Fault}}

To determine if the inspection processes find different risks, we looked at the total frequency of the types of risks found. We decided to use the risk type of the fault as opposed to using the class of fault (Missing, Wrong) as the fault type had more categories to chose from (A,B,C). We chose not to use the section in which the data was located and the item number as the data were mostly incomplete or incorrect.

The frequency of A, B and C risks found were tabulated against the inspection groups which found them. Any response that was not not applicable (NA) was discarded from the table. An example of this is found in table 3. In order to determine if they do find the same risks, a Chi-Square (CS) test of independence was performed on the tabulated results. The reason the CS was used was primarily because the data we wished to use were categorical and the frequency of each category was at least 5. Other tests, such as Fishers Exact Test were not applicable, for example, our table was greater than 2x2 rows. Fishers test should only be used for 2x2 tables.
